---
title: "ejv98_OriginalHomeworkCode_03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Challenge 1

```{r}
library(curl)
f<-curl(https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/zombies.csv")


d<-read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
# This loads the zombies dataset into the program
summary(d)
#Running summary() will show me the mean of every quantitative value from the population
MEANS FROM DATASET (given by summary(d))
height = 67.63
weight = 143.91
zombies killed = 2.992
years of education == 2.996
age = 20.05
```
```
#Challenge 2
```{r}
library(ggplot2)
library(gridExtra)
#height
x = ggplot(d, aes(x=gender, y=height)) +geom_boxplot()
x
#weight
y = ggplot(d, aes(x=gender, y=weight)) +geom_boxplot()
y
#zombies killed
g = ggplot(d, aes(x=gender, y=zombies_killed)) +geom_boxplot()
g
#education
c = ggplot(d, aes(x=gender, y=years_of_education)) +geom_boxplot()
c
#age
w = ggplot(d, aes(x=gender, y=age)) +geom_boxplot()
w
```
#Challenge 3
```{r}
library(ggplot2)
h = ggplot(d, aes(x=age, y=height)) +geom_point()
h
w = ggplot(d, aes(x=age, y=weight)) + geom_point()
w
<!-- Age, height, and weight are directly proportional (i.e. as age increases, so does height and weight) -->
```
#Challenge 4
```{r}
qqnorm(d$height)
qqnorm(d$weight)
qqnorm(d$age)
qqnorm(d$years_of_education)
<!-- not normal -->
qqnorm(d$zombies_killed)
<!-- not normal -->
<!-- Zombies killed and years of education are not normal. Looking at the qq plot, the loops do not make a linear line.  -->
```
#Challenge 5
```{r}
library(dplyr)
set.seed(1)
sam1 <- sample_n(d, 30, replace = FALSE)
summary(sam1) 
mean(sam1$height) 
mean(sam1$weight)
mean(sam1$zombies_killed)
mean(sam1$years_of_education)
mean(sam1$age)
sd(sam1$height)
sd(sam1$weight)
sd(sam1$zombies_killed)
sd(sam1$years_of_education)
sd(sam1$age)
se <- function(x) {sd(x)/sqrt(length(x))}
se(sam1$height)
se(sam1$weight)
se(sam1$zombies_killed)
se(sam1$years_of_education)
se(sam1$age)
quantile(sam1$height, c(0.025, 0.975))
quantile(sam1$weight, c(0.025, 0.975))
quantile(sam1$age, c(0.025, 0.975))
IC_Poisson <- function(x) {
 upper = mean(x) + 1.96 * sqrt(mean(x)/length(x))
 lower = mean(x) - 2.58 * sqrt(mean(x)/length(x))
 ci <- c(lower, upper)
 return(ci)
 }
```
#Challenge 6
```{r}


## Besides what you identified.. Good Job-WK